Handling missing data in smartphone location logs

### 2017-11-10 thesisReport.Rmd
started methods section

---
title: 'Research Report: Longitudinal models of human mobility'
author: "Boaz Sobrado"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography:
  - thesisGPS.bib
  - rReferences.bib
output:
  rmarkdown::pdf_document:
    fig_caption: yes        
    includes:  
      in_header: tp2.tex

@@

**Keywords: GPS, missing data, human mobility,big data**

@@

@@

For December, it would be nice to have the Lit Rev section, plus an exploration of the problem.

@@

The data used was collected between 2014 and 2017 on different Android devices. A total of X individuals contributed to the analysis, yielding a total of Y data points. Moreover we used diary information from **SOMEWHERE**.

Analyses were performed using R and a multitude of other packages (@ggplot2 @dplyr @leaflet @sp @ggthemes @base @sp1 @sp2).

*Plots: data points over time*

@@

#### Filtering

*Carlson et al 2015* describe a personal activity measurement system (PALMS), which can filter data points (among others). Their system is validated using cameras.

*Google* offers an out of the box activity inferral mechanism.

### Discussion on missing data

Our missing data patterns fit the broader pattern of missing data reported by others [@palmius_detecting_2017;@saeb_mobile_2015; @grunerbl_smartphone-based_2015;@harari_using_2016].

Missing data can  Importantly, one cannot say that the data is missing at random as there are a myriad of reasons why missingness can be related to location, such as turning off the phone on the plane before a long flight.

### Models

#### Spatiotemporal imputation methods

>>>>

---
title: 'Handling missing data in smartphone location logs'
author: "Boaz Sobrado"
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography:
  - thesisGPS.bib
  - rReferences.bib
output:
  rmarkdown::pdf_document:
    fig_caption: yes        
    includes:  
      in_header: tp2.tex

@@

@@

Missing: discussion of Barnett model.

@@

@@

The data used was collected between 2014 and 2017 on different Android devices from X individuals across X continents. The table below provides more details:

```{r datadetailsTable}
datadetails <- readRDS("datadetails.rds")
kable(datadetails,digits = 2,col.names = c("Log duration",
                                           "Observations",
                                           "Missing days",
                                           "Mean Accuracy",
                                           "SD Accuracy"))
```

Analyses were performed using R and a multitude of other packages [@ggplot2;@dplyr;@leaflet; @ggthemes;@base;@sp1;@sp2].

### Model evaluation
Models were evaluated using a test set and a train set. During a period of 7 days participants wore a professional GPS device (TRX-100) which reported location every minute. In addition, they continued using their phones as normal. Missing data was imputed for the week for which more accurate data was available.

Measures for which the accuracy was estimated include *barnett's path paper*.

@@
